---
title: "Rafael Uchoa de Lima's CV"
author: Rafael Uchoa de Lima
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'custom.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
library(fontawesome)
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/15cfamsUUlJDebm_VGFss17ewYXOxiN1F9f0uX9XklPg",  
  pdf_mode = params$pdf_mode
)

```
<!-- inicio academic icons -->
<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons@1/css/academicons.min.css">
<!-- final academic icons -->

 
<!-- inicio font awesome -->
<script src="https://kit.fontawesome.com/1f72d6921a.js" crossorigin="anonymous"></script>
<!-- final font awesome -->

<!-- inicio font Montserrat -->
<link rel="preconnect" href="https://fonts.googleapis.com">
<link rel="preconnect" href="https://fonts.gstatic.com" crossorigin>
<link href="https://fonts.googleapis.com/css2?family=Montserrat:wght@400;500;600;700&display=swap" rel="stylesheet">
<!-- final font Montserrat -->


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================


Contact {#contact}
--------------------------------------------------------------------------------

`r fa("envelope")` [rafaelulima@gmail.com](mailto:rafaelulima@gmail.com)

`r fa("github")` [GitHub](https://github.com/RafaelUL/)

`r fa("linkedin")` [LinkedIn](https://linkedin.com/in/rafaelul)

<div style="padding-bottom: 0.30in;"></div>


Technical Skills {#skills}
--------------------------------------------------------------------------------

`r fa("r-project")` `R (tidyverse, tidymodels, shiny)`

`r fa("python")` `Python (pandas, dash plotly, sklearn)`

`r fa("database")` `SQL`

`r fa("code-branch")` `Git`

`r fa("markdown")` `Markdown, Rmarkdown`


Languages {#languages}
--------------------------------------------------------------------------------

**English**: Fluent  

**Portuguese**: Fluent


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

```{r}
if(params$pdf_mode){
  cat("See this résumé [online](https://rafaelul.github.io/resume/index_en.html).")
} else {
  cat("[<i class='fas fa-download'></i> Download PDF](https://rafaelul.github.io/resume/cv_en.pdf).")
}
```

Made with the R packages [**pagedown**](https://github.com/rstudio/pagedown) and [**datadrivencv**](https://github.com/nstrayer/datadrivencv).

Source code available on `r fa("github")`  [GitHub](https://github.com/RafaelUL/resume).

```{r}
updated_string = stringr::str_glue("Last updated on {Sys.Date()}.")

if(params$pdf_mode){
  stringr::str_glue("{updated_string} The most recent version of this résumé is [available here](https://rafaelul.github.io/resume/cv_en.pdf).")
} else {
  cat(updated_string)
}
```


Main
================================================================================

Rafael Uchoa de Lima {#title}
--------------------------------------------------------------------------------


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```



Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('professional_experience')
```



Relevant Coursework {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('courses')
```

::: aside

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

```{r}
if(params$pdf_mode){
  cat("See this résumé [online](https://rafaelul.github.io/resume/index_en.html).")
} else {
  cat("[<i class='fas fa-download'></i> Download PDF](https://rafaelul.github.io/resume/cv_en.pdf).")
}
```

Made with the R packages [**pagedown**](https://github.com/rstudio/pagedown) and [**datadrivencv**](https://github.com/nstrayer/datadrivencv).

Source code available on `r fa("github")`  [GitHub](https://github.com/RafaelUL/resume).

```{r}
updated_string = stringr::str_glue("Last updated on {Sys.Date()}.")

if(params$pdf_mode){
  stringr::str_glue("{updated_string} The most recent version of this résumé is [available here](https://rafaelul.github.io/resume/cv_en.pdf).")
} else {
  cat(updated_string)
}
```

:::

